Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-22 manuscript/manuscript.Rmd
Small edits again

```{r figure2, dev="png", dpi=300, dev.args = list(type = "cairo-png"), out.width="400px", out.height="300px"}
#| fig.cap="Overall distribution of skill scores across models, including an ensemble of methods.
#|  Smaller scores are better (indicating smaller errors).
#|  Black bars indicate means, dots indicate all individual predictions over time and replicate 'true'
#| simulations of the given scenario."
shift |> 
  ggplot(aes(forecasting_model, score, color=forecasting_model)) + 
  geom_jitter(alpha = 0.06, show.legend = FALSE, shape=".") + 
  stat_summary(fun = mean, shape="|", show.legend = FALSE, col="black") +
  scale_x_discrete(limits = rev) +
  coord_flip() + 
  facet_grid(simulation ~ metric, scales = "free") + 
  scale_y_log10() +
  theme_bw() +
  theme(axis.title.y = element_blank())
```

>>>>

```{r figure2, dev="png", dpi=300, dev.args = list(type = "cairo-png"), out.width="400px", out.height="300px"}
#| fig.cap="Overall distribution of skill scores across models, including an ensemble of methods.
#|  Smaller scores are better (indicating smaller errors).
#|  Black bars indicate means. The points indicate all individual predictions over time and replicate 'true'
#|  simulations of the given scenario."
shift |> 
  ggplot(aes(forecasting_model, score, color=forecasting_model)) + 
  geom_jitter(alpha = 0.06, show.legend = FALSE, shape=".") + 
  stat_summary(fun = mean, shape="|", show.legend = FALSE, col="black") +
  scale_x_discrete(limits = rev) +
  coord_flip() + 
  facet_grid(simulation ~ metric, scales = "free") + 
  scale_y_log10() +
  theme_bw() +
  theme(axis.title.y = element_blank())
```
